% !TeX spellcheck = en_GB

\section{Planning and time organization}

	This whole project has been initially assigned in November 2018. Some research was done during the first half of 2019, but it was not fully addressed until September 2019. In order to explain the development of the tasks, these are listed below:
	
	\begin{itemize}
		\item Resources research: tasks related to the process of finding a database and a method to extract features. Also, the understanding of the whole feature extractor we use in the work can be included here.
		\item Previous works investigation: research about the current situation of the audio classification and how to implement a system with the obtained features.
		\item First attempts and experimentation: failed experiments and evolution of the designed system solution.
		\item Implementation of the final model: building the final system proposed and work to obtain the results.
		\item Assistance to meetings: assistance to meetings about the EMPATIA project
		\item Writing the report
	\end{itemize}

	In table \ref{table:14} a relation between the estimated time per task and the final amount of hours invested is included. It must be taken into account that in this time we are considering as well the time between the first period of the work defined above.
	
	\begin{table}[H]
		\begin{center}
			\begin{tabular}{|| m{10em} | m{7em} | m{7em} ||}
				\hline
				\textbf{Task} & \textbf{Estimation (h)} & \textbf{Actual time (h)} \\
				\hline\hline
				Resources research & 70 & 100 \\
				\hline
				Previous works investigation & 100 & 120 \\
				\hline
				First attempts and experimentations & 100 & 200 \\
				\hline
				Implementation of the final model & 160 & 160 \\
				\hline
				Assistance to meetings & 0 & 4 \\
				\hline
				Writing the report & 320 & 320 \\
				\hline
				TOTAL & \textbf{750} & \textbf{904} \\
				\hline
			\end{tabular}
		\end{center}
		\caption{Relation of estimated time and actual time invested  per task in hours}
		\label{table:14}
	\end{table}


\section{Economic resources}
	
	There are two main types of cost in to the development of this task. One of them is related to the material use and the other one to the recruitment. With respect to the first one, the only material that has been used is a computer \textit{MacBook Pro (Retina, 13 inches, End of 2013)}. The equivalent computer nowadays has a total price of 1.203,84 euros. Consider that a normal computer has a lifetime of 5 years of duration, that a month is composed by 160 hours of work and the number of total hours of work have been 904, we can deduce that the proportional price of the device is 113,36 euros without taxes.
	
	As for the staff costs, the people that have participated in this task is the student, as a researcher, and the professor, as a project manager. Also, some participation from the people in the TSC department can be included. Considering an average salary of a researcher in Spain of 1.286 euros per month, the salary for the student in case of being an official researcher would be 7.225,90 euros. Also, for the two participants of the department, considering they spent a total of 3 hours each, a salary of 24,1125 euros would correspond to the help of the researches \cite{Indeed2020}. 
	
	About the professor, considering that the period in which the project took place is approximately a year and that meetings of half an hour with the student took place averagely one time per week, if we also discard the two months of summer, an amount of 60 hours in meetings were invested by the professor. Also considering an extra time of 20 hours in the last part when working in the report, this gives a total of 80. If the average salary per month of a project manager in Spain is 2.217 euros, then a salary of 1.108,50 euros would correspond to the professor \cite{Indeed2020a}.
	
	In table \ref{table:15} the different expenses and salaries are included and also a final budget.
	
		\begin{table}[H]
		\begin{center}
			\begin{tabular}{|| m{10em} | m{7em} ||}
				\hline
				\textbf{Resource or worker} & \textbf{Cost (euros)} \\
				\hline\hline
				MacBook Pro & 113,36  \\
				\hline
				Assistant researcher & 24,1125 \\
				\hline
				Assistant researcher & 24,1125 \\
				\hline
				Main researcher & 7.225,90 \\
				\hline
				Professor & 1.108,50 \\
				\hline
				TOTAL & \textbf{8.495,99} \\
				\hline
			\end{tabular}
		\end{center}
		\caption{Relation of estimated time and actual time invested  per task in hours}
		\label{table:15}
	\end{table}
	

